### 2013-02-13 doc/xps2013/proposal.tex

>>>>

\paragraph{Concurrency Control: } Having too few tasks multiplexed per core fails to tolerate fully the latency; having too many increases memory and cache footprints, resulting in excess cache misses or exhausting physical memory unnecessarily.  Currently, we choose a number at program instantiation:  experiments so far have shown evidence of a broad sweet-spot, though it is of course varies as a function of application behavior.  At compile-time, we could estimate the number of tasks required based on the density of remote operations and hard-coded measurements of system characteristics; at runtime we can adjust the number of tasks dynamically based on real-time measurement of processor counters.  Exploring these directions may lead to even more robust performance.
